 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Saleh Talebizadeh}}}} % First name

	\vspace{6pt}

	{\Large Frontend $\sim$ Flutter Developer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	\icon{Globe}{11}{\href{https://zil.ink/mr_tz.dev}{zil.ink/mr\_tz.dev}}\\
	\icon{Phone}{11}{+98 937 351 5600}\\
	\icon{MapMarker}{11}{Kerman, Iran}\\

\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\icon{Envelope}{11}{\href{mailto:mstalebizadeh@gmail.com}{mstalebizadeh@gmail.com}}\\
	\icon{Github}{11}{\href{https://github.com/SalehTZ}{github.com/SalehTZ}}\\
	\icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/salehtz}{linkedin.com/in/salehtz}}\\

\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
	\cvsect{Summary}
	\vspace{-6pt}

	%Dummy text
	Mobile Application developer with six years of experience,
	including four years in Flutter and two years in Java.
	Skilled in transforming designs into user-friendly apps to enhance user satisfaction using Flutter,
	with a focus on continuous learning and a sustainable mindset.\\

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
	\cvsect{Skills}
	\vspace{-6pt}

	\begin{minipage}[t]{0.2\textwidth}
		\textbf{Languages:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.73\textwidth}
		Dart, Flutter, Java, SQL, Python, C++, C.
	\end{minipage}
	\vspace{4mm}

	\begin{minipage}[t]{0.2\textwidth}
		\textbf{Technologies:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.73\textwidth}
		Hive, RESTful, GraphQL, AppWrite, Firebase, RxDart, Git, Figma.
	\end{minipage}
	\vspace{4mm}

	\begin{minipage}[t]{0.2\textwidth}
		\textbf{Soft Skills:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.73\textwidth}
		Adaptability, Flexibility, Quick Learner, Passionate, Attention to detail
	\end{minipage}

\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
	{4/2023 -- Present\\\footnotesize{$\sim$9 months}}
	{Flutter Application Developer (Remote)}
	{Cateri, Kuwait}
	{\vspace{-10pt}
		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
			\item Created a \textbf{user-friendly} mobile app connecting users to local food trucks around Kuwait City.
			\item Implemented a custom \textbf{Map screen} with cool animations to make the user experience more enjoyable.
			\item Reduced food search time by half with \textbf{instant menu} access and precise truck \textbf{locations} on \textbf{Map}.
			\item Using \textbf{AppWrite} BaaS reduced costs and improved app functionality.
		\end{itemize}
		\texttt{Flutter} \slashsep \texttt{Maps} \slashsep \texttt{RESTful}}

	\entry
	{3/2019 -- 4/2023 \\\footnotesize{$\sim$4 years}}
	{Flutter Application Developer}
	{Freelance}
	{\vspace{-10pt}
		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
			\item Successfully completed multiple freelance projects for various clients, ranging from small utility applications to complex apps with intricate functionalities.
			\item Acquired an in-depth understanding of the complete app development cycle, from ideation and design to development, testing, and deployment.
			\item Created several personal apps for daily use, which are available on GitHub.
			\item Demonstrated diverse skills in developing functional, user-friendly, and visually appealing solutions.
		\end{itemize}
		\texttt{Flutter} \slashsep \texttt{Dart}}
	\entry
	{3/2017 -- 1/2019 \\\footnotesize{$\sim$2 years}}
	{Android Application Developer}
	{Freelance}
	{\vspace{-10pt}
		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
			\item Learned about developing Android apps through online courses and books.
			\item Completed various freelance projects for clients ranging from small utilities to complex apps.
			\item Created personal apps for daily use including mobile tools and editing apps
			\item Experience in developing Native Android apps has been both challenging and rewarding
		\end{itemize}
		\texttt{Java} \slashsep \texttt{Kotlin} \slashsep \texttt{XML}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
	\entry
	{Flutter}
	{Note App}
	{\url{https://github.com/SalehTZ/note_app_flutter}}
	{
		This project is a note-taking application developed using the Flutter framework, with Hive serving as the database. The application empowers users to effortlessly create, delete, and edit notes, providing a seamless and efficient note-taking experience.
	}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
	\entry
	{9/2016 - 9/2020}
	{Computer Science }
	{Shahid Bahonar University of Kerman}
	{Studied Computer Science at SBUK}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Languages}
\vspace{-6pt}

\hspace{26mm} \textbf{English} - Advanced , \textbf{ Persian} - native

%----------------------------------------------------------------------------------------

\end{document}
